---
title: "Cabbages"
author: "Genevieve Berumen"
date: "Fall2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions 
 $H_0$ There is no difference in vitiam C cintent between cultivation c39 and c52

 $H_A$ A statistically significant amount of vitamin C exists in either cultivation c39 or c52. 
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy) 
+ geom_boxplot(fill = "lavender", outlier.colour = "red", outlier.shape = 1, notch = TRUE) +
  labs(x = "Cultivar", y = "Vitamin C")
 theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Per box plot, C52 shows a higher level of vitC C. Culture 39 has a lower level. By looking at the two boxes you can clearly see they are disjointed, indicating a high probability of a significant difference.  


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```
The data shows that Q3 of C39 is smaller tha the Q1 of C52 indicating that they are indeed disjointed. 




## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
The p-value of 0.00000003405 provides strong evidence of a significant difference between C39 and C52.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


In my analysis, I created a boxplot chart to visually examine and compare the Vitamin C levels across various cultivar groups. The chart allowed me to gain insights into the central tendency, variability, and potential outliers in the Vitamin C data for each specific cultivar. When notches were included and did not overlap, it indicated statistically significant differences in median Vitamin C levels among the cultivar groups, making it easy for me to make meaningful comparisons between these groups.


